\rmtab{
\textbf{Login}\newline
[R1] The system must allow students to log-in through their academic email and password, if they provide them correctly.\newline
[R2] Only students with an academic credential provided by a registered university can log-in.
}{
WebApp \newline
AuthenticationManager\newline
SheerId API\newline
DAO\newline
Database
}

\rmtab{
\textbf{Edit profile}\newline
[R3] The system must allow the student to edit his profile info, remove the CV and add a new version of the CV.\newline
[R4] The student can edit only his profile.
}{
WebApp \newline
AuthenticationManager \newline
AccountManager \newline
DAO \newline
Database
}

\rmtab{
\textbf{Internship recommendation}\newline
[R5] The system must send an email to the student when an internship that might interest him
becomes available.
}{
Affinity Analyzer\newline
DAO\newline
Database\newline
Notification Manager\newline
Mail Service
}

\rmtab{
\textbf{Search an internship}\newline
[R6] The system must provide to the student all internships satisfying search criteria.\newline
[R7] The system must provide to the student only internships satisfying search criteria.
}{
WebApp\newline
Internship Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Apply for an internship}\newline
[R8] The system must register the student’s application for the internship.\newline
[R9] The system must register only applications of students who have submitted an application for
the internship.
}{
WebApp\newline
Internship Manager\newline
DAO\newline
Database
}\rmtab{
\textbf{Answer interview questions}\newline
[R10] The student must be able to answer interview questionnaires.\newline
[R11] The student can answer interview questionnaires regarding only internships he’s applied for
and accepted by the involved company.
}{
WebApp\newline
Contract Manager\newline
Interview Manager\newline
DAO\newline
Database
}\rmtab{
\textbf{Consulting CV suggestion}\newline
[R12] The student must be able to view suggestions on how to improve his CV.\newline
[R13] The student can view suggestions regarding only his CV.
}{
CV Analyzer\newline
Notification Manager\newline
Mail Service\newline
DAO\newline
Database
}
\rmtab{
\textbf{Registration and login}\newline
[R14] The system must allow companies to register to S\&C providing mandatory data (name, email,
VAT number) and selecting a password.\newline
[R15] The system must allow registered companies to log-in through their email and password, if they are provided correctly.
}{
WebApp\newline
Authentication Manager\newline
DAO\newline
Database
}\rmtab{
\textbf{Upload an internship}\newline
[R16] The system must allow the company to fill an internship creation form.\newline
[R17] The system must allow the company to select the internship type.\newline
[R18] The system must allow the company to select the internship duration.\newline
[R19] The system must allow the company to select if the internship is paid or not.\newline
[R20] The system must allow the company to select the skills it is searching for in the candidates.
}{
WebApp\newline
Internship Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Student recommendation}\newline
[R21] The system must send an email notifying the company when a student with a CV corresponding
to their needs becomes available.
}{
Mail Service\newline
Notification Manager\newline
Affinity Analyzer\newline
DAO\newline
Database
}
\rmtab{
\textbf{Interview students}\newline
[R22] The company must be able to provide structured questionnaires to students.\newline
[R23] The company can provide structured questionnaires only to students who have applied to an internship uploaded by the company itself.\newline
[R24] The company must be able to view answers to questionnaires it created.
}{
WebApp\newline
Contract Manager\newline
Interview Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Create contract}\newline
[R25] The company must be able to register a contract regarding an internship and referring to the assigned student.\newline
[R26] The company can register contracts regarding only internships uploaded by the company itself. \newline
[R27] The company can register contracts referring only to students that have applied for the indicated internship.
}{
WebApp\newline
Contract Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Login}\newline
[R28] The system must allow registered universities to log-in through credentials provided by S\&C,
if they are provided correctly.
}{
WebApp\newline
Authentication Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Terminate an internship}\newline
[R29] The system must allow universities to terminate an internship involving their students.
}{
WebApp\newline
Contract Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Leave a feedback}\newline
[R30] The student must be able to post feedback.\newline
[R31] The company must be able to post feedback.\newline
[R32] Only students that have participated in an internship can leave feedback for it.\newline
[R33] Only companies that have participated in an internship can leave feedback for it.\newline
[R34] Every student can leave at most one feedback per internship.\newline
[R35] Every company can leave at most one feedback per internship.\newline
}{
WebApp\newline
Contract Manager\newline
Feedback Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Open discussion}\newline
[R36] The student must be able to open a discussion with the company he’s interning with and the
university he’s enrolled at.\newline
[R37] The company must be able to open a discussion with the students they are collaborating with
and universities those students are enrolled at.\newline
[R38] The student can open a discussion only with the company he’s interning with and the university
he’s enrolled at.\newline
[R39] The company can open a discussion only with students they are collaborating with and universities.
}{
WebApp\newline
Contract Manager\newline
Discussion Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Send and receive messages within a discussion}\newline
[R40] The student can send and receive messages only from a discussion he is participating in.\newline
[R41] The company can send and receive messages only from a discussion it is participating in.\newline
[R42] The university can send and receive messages only from a discussion it is participating in.
}{
WebApp\newline
Contract Manager\newline
Discussion Manager\newline
DAO\newline
Database
}
\rmtab{
\textbf{Monitor the status of the internship}\newline
[R43] The student must be able to monitor the status of the internships in which he has applied.\newline
[R44] The company must be able to monitor the status of the internships it has published.\newline
[R45] The university must be able to monitor the status of the internship in which its students have applied.
}{
WebApp\newline
Contract Manager\newline
DAO\newline
Database
}